\newcommand{\enablePageBorder}{1}
\newcommand{\enablePageHeader}{0}
\newcommand{\pageBorderBegin}{0}

\input{common/env/printer}
\input{common/env/common}
\input{common/text}

\setlength{\parindent}{0pt}

% document %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
\defaultFontSize

\pagestyle{empty}

\vspaceLarge\titleMajor{Ad Completórium}
\vspaceLarge

\input{common/usual-beginning}
\vfill

\subTitle{Inčipit Ordo Psalmodiae}~~\subTitleNote{—~~et post hunc. . .}
\vfill

% TODO: diacritics
\subTitle{Te Lučis Ànte Tèrminum}\vspaceMedium

\prayerText{\firstLetter{T}e lucis ante términum, \symbolBreak Rerum Creátor, póscimus, \symbolBreak ut pro tua cleméntia \symbolBreak sis praesul et custódia.}\vspaceMedium

\prayerText{\firstLetter{P}rocul recédant sómnia, \symbolBreak et nóctium phantásmata; \symbolBreak hostémque nostrum cómprime, \symbolBreak ne polluántur córpora.}\vspaceMedium

\prayerText{\firstLetter{P}raesta, Pater piíssime, \symbolBreak Patríque compar Únice, \symbolBreak cum Spíritu Paráclito \symbolBreak regnans per omne sáeculum.}\vspaceMedium

\prayerText{\firstLetter{A}men.}\vspaceSmall

\newpage

\prayerVersicleResponse
% Now, as the day turns to its end, I give thanks to Thee, O Lord, and I pray that the evening and the night may be without sin. Grant this to me, O Savior, and save me."
{Nunc die ad tèrminum vergènte, gráçias tìbi ago, Domine, et prècor ut vèspera et nox sine peccáto sint. Cončéde hoc mìhi, Salvátor, et sàlva me.}
{\textGloriaPatri}\vspaceMedium

\prayerVersicleResponse
% Now, the day having passed into darkness, I glorify Thee, O Lord, and I pray that the evening and the night may be without stumbling. Grant this to me, O Savior, and save me.
{Nunc die in tènebras trànsito, te glorifico, Domine, et prècor ut vèspera et nòx sine scàndalo sint. Cončéde hoc mìhi, Salvátor, et sàlva me.}
{\textEtNuncEtSemper}\vspaceMedium

% Now, the day having been led to its end, I praise Thee, O Holy One, and I pray that the evening and the night may be without disturbance. Grant this to me, O Savior, and save me.
\prayerVersicle{Nunc die ad finem perdùcto, te laudo, Sancte, et prècor ut vèspera et nox sine perturbaçióne sint. Cončéde hoc mìhi, Salvátor, et sàlva me.}\vfill

% Lord our God, whatever sins I have committed this day, whether word, or deed, or thought, forgive me, for you are good and love all people. Grant me a peaceful and undisturbed sleep. Protect me from every abuse and plot of the evil one. Raise me up in due time that I may glorify you, for you are blessed, together with your only begotten Son and your all holy Spirit, now and forever and to the ages of ages. Amen.
\prayerText{\firstLetter{D}òmine Deus noster, quaecùmque hódie peccavi, sive vèrbo sìve ópere sive coǧitaçione, remìtte mìhi, quia bonus es et amátor hòminum. Cončéde mìhi sòmnum pačìficum et imperturbátum. Consèrva me ab òmni insùltu et insìdiīs Malìgni. Èxčita me tèmpore opportúno ad glorificàndum te, quia benedìctus es, cum Uniǧènito Fílio tuo et Sanctìssimo Spíritu tuo, nunc et sèmper et in sáecula saeculórum. Amen.}\vfill

\prayerText{\input{common/prayers/symbolum-fidei/1}}\vspaceMedium

\prayerText{\input{common/prayers/symbolum-fidei/2}}\vspaceMedium

\prayerText{\input{common/prayers/symbolum-fidei/3}}\vspaceMedium

\prayerText{\input{common/prayers/symbolum-fidei/4}}\vspaceMedium

\newpage

% Thou who at every time and hour, in Heaven and on earth art worshipped and glorified, O Christ our God; long-suffering, merciful and compassionate; who lovest the just and showest mercy to sinners; who callest all to salvation through the promise of future good things. O Lord, in this hour receive our supplications, and direct our lives according to Thy commandments. Sanctify our souls, purify our bodies, Correct our minds and cleanse our thoughts, and deliver us from all tribulations, evil and distress. Surround us with Thy holy angels, that, guided and guarded by them, we may attain to the unity of the faith and the knowledge of thine unapproachable glory, for Thou art blessed unto ages of ages. Amen
\prayerText{\firstLetter{T}u qui òmni tèmpore et hora, in čaelo et in tèrra, adoráris et glorificáris, Christe Deus noster; qui longànimis, mùltum mizèricors, et compàtiens; qui ïustos díliǧis et peccatórum mizeráris; qui òmnes ad salútem vocas per promissiónem bonórum futurórum. Súsčipe, Dòmine, in hāc hora prèces nostras, et díriǧe vitam nostram ad mandáta tua. Sanctìfica ànimas nostras, častìfica còrpora, coǧitaçiónes còrriǧe et purìfica mèntes, et líbera nos ab òmni tribulaçióne, màlo et dolóre. Çircùmda nos ànǧelīs sanctīs tuis, ut,
custóditi et dedùcti ab eīs, perveniámus ad unitátem fidéi et sčiènçiam inacčessìbilis glóriae tuae, quia benedìctus es in sáecula saeculórum. Amen.}\vfill

\prayerText{\input{common/prayers/axion-estin}}\vfill

\prayerText{\input{common/prayers/trisagion}} \hspace{0.5em} {\fmtPrayerRepeatText (iij.)}\vfill

\prayerVersicleResponseGloriaPatri\vfill

\prayerText{\input{common/prayers/sanctissima-trinitas}}\vfill

\prayerText{Kýrie eléison.} \hspace{0.5em} {\fmtPrayerRepeatText (iij.)}\vfill

\prayerVersicleResponseGloriaPatri\vfill

\prayerText{\input{common/prayers/pater-noster}}\vfill

\prayerVersicleResponse
{Dòmine Ïesu Christe, Deus noster, mizerére nostri et salva nos.}
{Amen.}\vspaceSmall

\newpage

\prayerText{\input{common/prayers/ave-maria}}\vspaceMedium

\prayerVersicleResponseGloriaPatri\vspaceMedium

\prayerVersicleResponse
{Per oraçiónes sanctórum patrum nostrórum, Dómine Ïesu Christe, Deus noster, mizerére nostri et salva nos.}
{Amen.}\vspaceMedium

\prayerVersicleResponse
{Dòmine, exáudi oraçiónem meam.}
{Et clamor meus ad te vèniat.}\vspaceMedium

\prayerVersicleResponse
{Benedicámus Dòmino.}
{Deo gráçias.}\vspaceMedium

\prayerVersicleResponse
{Fidélium ànimae per mizericórdiam Dei requiésçant in pače.}
{Amen.}\vfill

\prayerVersicle{Orémus.}\vfill

% Now, O Lord our God, grant unto us in the sleep that follows, rest of body and soul, and keep us from the dark sleep of sin and from every dark and nocturnal sensuality. Restrain the impulses of the passions, extinguish the fiery darts of the evil one, craftily hurled against us; soothe the disturbances of our flesh, and lull to sleep all earthly and material thoughts. Grant unto us, O most merciful God, a watchful mind, a chaste reason, a sober heart, and a tranquil sleep, free from every evil fantasy. At the hour of prayer, awaken us, that being confirmed in Thy commandments, we may be ever mindful of Thy judgments. And grant, we beseech Thee, that through the whole night we may be able to glorify Thee, so that we may sing to, bless, and glorify Thy most honored and majestic name: of the Father, and of the Son, and of the Holy Spirit, now and ever, and unto ages of ages.
\prayerText{\firstLetter{N}unc, Dòmine Deus noster, cončéde nobīs in sòmno sequènti, requiem còrporis et ànimae, et custódi nos a tenebróso sòmno peccáti et ab omni obscura ac nocturna sensuali. Cóhibe ìmpetūs passiónum, exstìngüe tela malìgni igníta, dolóse còntra nos emìssa; mìtiga turbaçiónem carnis nostrae, et sopi coǧitaçiónes terrénas ac materiáles. Práesta nobīs, Deus piìssime, mèntem viǧilàntem, raçiónem càstam, cor sóbrium, et sòmnum tranquìllum, ab òmni fantàzia màla líberum. Ad horam oraçiónis èxčita nos, ut in mandátīs tuīs confirmáti ïudičiórum tuórum simus sèmper mèmores. Et práesta, quaesumus, ut per totam nòctem te glorificáre valeámus, ita ut nomen tuum honoratìssimum ac maïestáticum cantémus, benedicámus, et glorificémus~: Pàtris, et Fílii, et Spíritūs Sancti, nunc et sèmper et in sáecula saeculórum.}\vspaceMedium

\prayerResponse{Amen.}\vspaceMedium

\newpage

% Lord, Lover of mankind, forgive those who hate and persecute us; do good to those who do good to us, and grant them all things necessary for salvation and eternal life. Visit the sick, and grant them health. Guide those at sea; travel with those who journey. Assist our authorities in every good work for the peace of the world. Grant remission of sins to those who serve us and those who have mercy on us. In the multitude of Thy mercy, have mercy on those who, through us unworthy ones, entreat Thee for themselves. Remember, O Lord, our departed brothers and sisters, and grant them rest where the light of Thy countenance shines upon them. Remember, O Lord, our brothers who are in captivity, and preserve them from every evil. Remember those who do good to Thy churches, and grant them salvation and eternal life. Remember also, O Lord, us humble and sinful and unworthy servants of Thine. Enlighten our minds with the light of Thy knowledge and lead us in the way of Thy commandments; through the intercessions of our most pure Lady, Mother of God and ever-virgin Mary, and of all Thy saints, for blessed art Thou unto the ages of ages.
\prayerText{\firstLetter{D}òmine, Amátor hòminum, remìtte odièntibus et persequèntibus nos; bènefač eīs qui benefáčiunt nobīs, et dóna eīs òmnia ad salútem et vitam aetèrnam nečessária. Vísita infìrmos, et praesta sanitátem ìllīs. Díriǧe navigàntes; comitáre ìter fačièntes. Assìste potestátibus nostrīs in òmni ópere bono ad pačem mùndi. Praesta remissiónem peccatórum eīs qui sèrviunt nobīs et qui nostri mizerèntur. In multitúdine mizeraçiónis tuae, mizerére eórum qui per nos indìgnos te deprecàntur pro se. Memènto, Dòmine, fratrum et sorórum nostrárum defunctórum, et rèquiem eīs cončéde, ubi super eos fùlǧet lux vùltus tui. Memènto, Dómine, fratrum nostrórum qui sunt in captivitáte, et consèrva eos ab òmni màlo. Memènto eórum qui benefàčiunt ecclésiīs tuīs, et dóna ìllīs salútem et vitam aetèrnam. Memènto ètiam, Dòmine, nostrum humìlium et peccatórum et indignórum servórum tuórum. Illúmina mèntes nostras lúmine sciènçiae tuae et dedúce nos in via mandatórum tuórum; per interčessiónes Dòminae nostrae purìssimae, Dei Matris ac semper Vìrǧinis Maríae, et òmnium sanctórum tuórum, quia benedìctus es in sáecula saeculórum.}\vspaceMedium

\prayerResponse{Amen.}\vspaceMedium

\begin{center}
\symbolCross
\end{center}

\vfill\vfill

\end{document}
