% Thee, as God, we praise: Thee, as Lord, we confess. Thee, the eternal Father, all the earth venerates. To Thee all angels, to Thee the heavens and all powers: to Thee Cherubim and Seraphim, with unceasing voice cry out: Holy, Holy, Holy, Lord God of Hosts. Full are the heavens and the earth of the majesty of Thy glory.
\prayerText{\firstLetter{T}e Deum laudámus: te Dòminum confitémur. Te aetèrnum Pàtrem òmnis tèrra venerátur. Tìbi òmnes Ànġeli; tìbi caeli et univèrsae Potestátes; Tìbi Ċerubína et Serafína inċessábili voċe proclámant: «~Sanctus, Sanctus, Sanctus, Dòminus Deus Sàbaot.~» Pleni sunt ċaeli et tèrra majestátis glóriae tuae.}\vspaceMedium

% Thee, the glorious choir of Apostles, Thee, the laudable number of Prophets, Thee, the white-robed army of Martyrs praises. The holy Church throughout the circle of the earth confesses Thee: The Father of boundless majesty; Thy venerable, true, and only Son; and also the Holy Spirit, the Paraclete.
\prayerText{\firstLetter{T}e gloriósus Apostolórum chorus, te Profetárum laudábilis númerus, te Màrtyrum candidátus laudat exèrċitus. Te per orbem terrárum sancta confitétur Ecclésia: Pàtrem immènsae majestátis; veneràndum tuum verum et únicum Fílium; Sanctum quoque Paràclitum Spíritum.}\vspaceMedium

% Thou art the King of Glory, O Christ. Thou art the Father's everlasting Son. Thou, about to take on man to set him free, didst not abhor the Virgin’s womb. Thou, having conquered the sting of death, hast opened to believers the kingdoms of heaven. Thou art believed to be the Judge about to come. We therefore pray Thee, help Thy servants, whom Thou hast redeemed with Thy precious blood. Make them to be numbered with Thy saints in eternal glory.
\prayerText{\firstLetter{T}u Rex glóriae, Christe. Tu Pàtris sempitèrnus es Fílius. Tu ad liberàndum susçeptúrus hòminem, non horruìsti Vìrġinis úterum. Tu, devìcto mortis acúleo, aperuìsti credèntibus regna ċaelórum. Tu ad dèxteram Dei sedes, in glória Pàtris. Judex créderis èsse ventúrus. Te èrgo quáesumus, tuīs fàmulīs sùbveni: quos preçióso sànguine redemìsti. Aetèrna fac cum sanctīs tuīs in glória numerári.}\vspaceMedium

% Make safe Thy people, O Lord, and bless Thy inheritance. Rule them, and lift them up even unto eternity. Through individual days we bless Thee; And we praise Thy name unto the age, and unto the age of ages.
\prayerText{\firstLetter{S}àlvum fac pòpulum tuum, Dòmine, et benedíce hereditáti tuae, et reġe eos, et extòlle ìllos ùsque in aetèrnum. Per sìngulos dies benedícimus te, et laudámus nomen tuum in sáeculum, et in sáeculum sáeculi.}\vspaceMedium

% Vouchsafe, O Lord, on this day to keep us without sin. Let Thy mercy, O Lord, be upon us, just as we have hoped in Thee. In Thee, O Lord, I have hoped: let me not be confounded unto eternity.
\prayerText{\firstLetter{D}ignáre, Dòmine, die ìsto sine peccato nos custodíre. Mizerére nostri, Dòmine, mizerére nostri. Fiat mizericórdia tua, Dòmine, super nos, quemàdmodum sperávimus in te. In te, Dòmine, sperávi: non confùndar in aetèrnum.}
