\chead{\sc{\formatTextHeader Oraçiónes Vàriae}}
\markboth{}{}

\begin{center}
\vspace*{-1.0\baselineskip}

{\formatTextPsalmChapter ORAÇIÓNES VÀRIAE}

\vspaceSmall
\end{center}

\prayerTitle{Sỳmbolum Fidéi}

\psalmText{\input{common/prayers/symbolum-fidei/1}}\vspaceMedium

\psalmText{\input{common/prayers/symbolum-fidei/2}}\vspaceMedium

\psalmText{\input{common/prayers/symbolum-fidei/3}}\vspaceMedium

\psalmText{\input{common/prayers/symbolum-fidei/4}}

\vfill

\prayerTitle{Precàçio Ïesu}

\psalmText{\firstLetter{D}òmine Ïesu Christe, Fili Dei, miserére mei, peccatóris.}

\vfill

\newpage

\prayerTitle{Ad Matutínum}

% Morning prayer of St. Basil
% We bless you, O God, Most High and Lord of Mercy, who always work great and inscrutable things, glorious and innumerable wonders with us. You grant sleep to us for rest from our infirmities, and quiet from the burdens of the flesh that is laboring greatly. We give thanks to you, because you have not lost us on account of our sins, but have remained in your love; and when we had fallen into despair, you raised us up to glorify your power. Therefore, we beseech your incomparable goodness: illuminate the eyes of our understanding, and lift our minds from the heavy sleep of laziness. Open our mouth and fill it with your praise, so that without distraction we may be able to sing and confess that you are God, glorified in all and through all, the Eternal Father, with your Only-Begotten Son, and your Most Holy, good, and life-giving Spirit, now and always, and forever and ever.
\prayerText{\firstLetter{B}enedícimus te, Deus, Altìssime et Dòmine misericórdiae, qui sèmper nobíscum operáris màgna et inscrutabìlia, gloriósa ac mirabìlia innumerabìlia. Tu nobīs sòmnum larǧíris ad rèquiem ab infirmitátibus nostrīs, et quiétem ab onèribus carnis multum laboràntis. Gráçias tìbi àgimus, quia non perdidìsti nos pròpter peccáta nostra, sed in tua dilecçióne permansìsti~; et quum in desperaçiónem lapsi essémus, erexìsti nos ad glorificàndam virtútem tuam. Ìdeo tuam bonitátem incomparábilem deprecámur: illúmina òculos intelléctūs nostri, et lèva mèntes nostras de gràvi sòmno desìdiae. Àperi os nostrum et ìmple ìllud laude tua, ut sine distracçióne valeámus cantáre et confitéri te esse Deum, glorificátum in òmnibus et per òmnia, Pàtrem aetèrnum, cum Uniǧènito Fílio tuo, et Spíritu tuo sanctìssimo, bono et vivìfico, nunc et sèmper, et in sáecula saeculórum. Amen.}

\vfill\vfill

\prayerTitle{Ad Completórium}

% Now, O Lord our God, grant unto us in the sleep that follows, rest of body and soul, and keep us from the dark sleep of sin and from every dark and nocturnal sensuality. Restrain the impulses of the passions, extinguish the fiery darts of the evil one, craftily hurled against us; soothe the disturbances of our flesh, and lull to sleep all earthly and material thoughts. Grant unto us, O most merciful God, a watchful mind, a chaste reason, a sober heart, and a tranquil sleep, free from every evil fantasy. At the hour of prayer, awaken us, that being confirmed in Thy commandments, we may be ever mindful of Thy judgments. And grant, we beseech Thee, that through the whole night we may be able to glorify Thee, so that we may sing to, bless, and glorify Thy most honored and majestic name: of the Father, and of the Son, and of the Holy Spirit, now and ever, and unto ages of ages.
\prayerText{\firstLetter{N}unc, Dòmine Deus noster, cončéde nobīs in sòmno sequènti, requiem córporis et ànimae, et custódi nos a tenebróso sòmno peccáti et ab omni obscura ac nocturna sensuali. Cóhibe ìmpetūs passiónum, exstìngüe tela malígni igníta, dolóse còntra nos emìssa; mìtiga turbaçiónem carnis nostrae, et sopi coǧitaçiónes terrénas ac materiáles. Práesta nobīs, Deus piìssime, mèntem viǧilàntem, raçiónem càstam, cor sóbrium, et sòmnum tranquìllum, ab òmni fantàsia màla líberum. Ad horam oraçiónis èxčita nos, ut in mandátīs tuīs confirmáti ïudičiórum tuórum simus sèmper mèmores. Et práesta, quaesumus, ut per totam nòctem te glorificáre valeámus, ita ut nomen tuum honoratìssimum ac maïestáticum cantémus, benedicámus, et glorificémus~: Pàtris, et Fílii, et Spíritūs Sancti, nunc et sèmper et in sáecula saeculórum. Amen}

\vfill

\newpage

\prayerTitle{Sancti Ambrósii Ante Eucharìstiam}

% LORD Jesus Christ, I approach Thy banquet table in fear and trembling, for I am a sinner, and dare not rely on my own worth, but only on Thy goodness and mercy. I am defiled by my many sins in body and soul, and by my unguarded thoughts and words. Gracious God of majesty and awe, I seek Thy protection, I look for Thy healing. Poor troubled sinner that I am, I appeal to Thee, the fountain of all mercy. I cannot bear Thy judgment, but I trust in Thy salvation. Lord, I show my wounds to Thee and uncover my shame before Thee. I know my sins are many and great, and they fill me with fear, but I hope in Thy mercies, for they cannot be numbered.
\prayerText{\firstLetter{A}d mènsam dulčìssimi convívii tui, pie Dòmine Ïesu Christe, ego peccátor de pròpriīs meīs mèritīs nìhil praesúmens, sed de tua confídens misericórdia et bonitáte, acčédere vèreor et contremísčo. Nam cor et córpus hàbeo mùltis crimìnibus maculátum, mèntem et lìngüam non caute custodítam. Ergo, o pia Déitas, o tremènda maïèstas, ego mìser, ìnter angùstias deprehènsus, ad te fòntem misericórdiae recùrro, ad te festíno sanàndus, sub tuam protecçiónem fúǧio; et quem Ïúdičem sustìnere néqueo, Salvatórem hàbere suspíro. Tìbi, Dòmine, plagas meas ostèndo, tìbi verecùndiam meam déteǧo. Sčio peccáta mea mùlta et màgna, pro quìbus tìmeo; spero in misericórdias tuas, quarum non est númerus.}

\vfill

% LORD Jesus Christ, Eternal King, God and man, crucified for mankind, look upon me with mercy and hear my prayer, for I trust in Thee. Have mercy on me, full of sorrow and sin, for the depth of Thy compassion never ends. PRAISE to Thee saving sacrifice, offered on the wood of the cross for me and for all mankind. Praise to the noble and precious Blood, flowing from the wounds of my crucified Lord Jesus Christ and washing away the sins of the whole world. 
\prayerText{\firstLetter{R}èspiče èrgo in me òculis misericórdiae tuae, Dòmine, Ïesu Christe, Rex aetèrne, Deus et homo, cručifíxus pròpter hòminem. Exáudi me speràntem in te; miserére mei pleni misèriīs et peccátīs, tu qui fòntem miseraçiónis nùmquam manáre čessábis. Sàlve, salutáris vìctima, pro me et òmni humáno ǧènere in patìbulo Cručis obláta. Sàlve, nóbilis, et preçióse sàngüis, de vulnèribus cručifíxi Dòmini mei Ïesu Christi prófluens, et peccáta tótius mùndi àbluens.}

\vfill

% REMEMBER, Lord, Thy creature, whom Thou hast redeemed with Thy blood; I repent my sins, and I long to put right what I have done. Merciful Father, take away all my offenses and sins; purify me in body and soul, and make me worthy to taste the Holy of Holies. May Thy Body and Blood, which I intend to receive, although I am unworthy, be for me the remission of my sins, the washing away of my guilt, the end of my evil thoughts, and the rebirth of my better instincts. May it incite me to do the works pleasing to Thee, and a firm defense of body and soul against the wiles of my enemies. Amen. 
\prayerText{\firstLetter{R}ecordáre, Dòmine, creatúrae tuae, quam tuo sàngüine redemìsti. Póenitet me peccavìsse, cúpio emendáre quod feči. Aufer èrgo a me, clementìssime Pàter, òmnes iniquitátes et peccáta mea; ut, purificátus mènte et córpore, dìgne degustáre mèrear Sancta Sanctórum. Et cončéde, ut haec sancta praelibáçio córporis et sàngüinis tui, quam ego indìgnus súmere intèndo, sit peccatórum meórum remìssio, sit delictórum perfècta purgáçio, sit tùrpium coǧitaçiónem effugáçio ac bonórum sènsuum regeneráçio, operùmque tìbi plačèntium salúbris efficáčia, ànimae quoque et córporis còntra inimicórum meórum insìdias firmìssima tuìçio. Amen.}

\newpage

\prayerTitle{Sancti Ïohànnis Chrysòstomi Post Eucharìstiam}

\prayerText{\firstLetter{G}ràçias tìbi àǧimus, clementìssime Dominátor, Redèmptor animárum nostrárum, quóniam et praesènti hac die coelèstibus et immortálibus mystériis nos dìgnos fečìsti. Tu díriǧe viam nostram; sèrva nos in timóre tuo; tuére vitam nostram; grèssus nostros fìrma oraçiónibus et interčessiónibus sanctae et gloriósae Dei Ǧenetríčis et sèmper Vìrǧinis Maríae. Exaltáre super čoelos, Deus, et super òmnem tèrram glória tua nunc et sèmper, et in sáecula saeculórum. Amen.}

\vfill

\prayerTitle{Sancti Efraími Sỳri}

\psalmText{\input{common/prayers/lenten-st-ephraim/0}}

\vfill

\prayerTitle{Sancti Benedìcti}

\psalmText{\input{common/prayers/sancti-benedicti.tex}}

\vfill

\prayerTitle{Ave María}

\psalmText{\input{common/prayers/ave-maria.tex}}

\newpage

\prayerTitle{Àlma Redemptóris Mater}

\psalmText{\input{common/prayers/alma-redemptoris-mater.tex}}

\vfill

\prayerTitle{Ave Reǧína Coelórum}

\psalmText{\input{common/prayers/ave-regina-coelorum.tex}}

\vfill

\prayerTitle{Reǧína Coeli}

\psalmText{\input{common/prayers/regina-coeli.tex}}

\vfill

\prayerTitle{Sàlve Reǧína}

\psalmText{\input{common/prayers/salve-regina.tex}}

\vfill

\prayerTitle{Àxion Èstin}

\psalmText{\input{common/prayers/axion-estin.tex}}
