\antiphonDayOfWeek
{Domìnica I,}
{Psàlmus XI.}
{in tono primo~:}
% Now will I arise, says the Lord. I will set him in safety: I will deal confidently in his regard.
{«~Nunc exsùrǧem~», dičit Dòminus; «~Ponem in salutári~; fidučiáliter àǧem in eo.}
% The words of the Lord are pure words.
{Elóquia Dòmini, elóquia čàsta}
{«~Nunc exsùrǧem~», dičit Dòminus.}
{ «~Ponem in salutári~; fidučiáliter àgem in eo}\vspaceLarge\newpage

\antiphonDayOfWeek
{Domìnica II,}
{Psàlmus VII.}
{in tono secùndo~:}
% Arise, O Lord, my God, in the precept which thou hast commanded, and a congregation of people shall surround thee.
{Exsùrǧe, Dòmine Deus meus, in praečèpto quod mandavìsti, et synagóga populórum çircùmdabit te.}
% Rejoice in the Lord, O you just: praise is fitting for the upright. 
{Dòmine, Deus meus, in te sperávi~; sàlvum me fac.}
{Exsùrǧe, Dòmine Deus meus, in praečèpto quod mandavìsti.}
{Et synagóga populórum çircùmdabit te.}\vspaceLarge

\antiphonDayOfWeek
{Domìnica III,}
{Psàlmus XCV.}
{in tono tèrçio~:}
% Say among the Gentiles, the Lord has reigned. For he has corrected the world, which shall not be moved.
{Díčite in ǧèntibus: «~Dòminus regnávit~». Ètenim corréxit orbem tèrrae qui non commovébitur.}
% Sing to the Lord a new canticle: sing to the Lord, all the earth.
{Čantáte Dòmino čànticum novum~; čantáte Dòmino, òmnis tèrra.}
{Díčite in ǧèntibus: «~Dòminus regnávit~».}
{Ètenim corréxit orbem tèrrae qui non commovébitur.}\vspaceLarge

\antiphonDayOfWeek
{Domìnica IV,}
{Psàlmus XLIII.}
{in tono quarto~:}
% Arise, O God, help us, and redeem us according to your name.
{Exsùrge, Dòmine, àdjuva nos, et rèdime nos pròpter nomen tuum.}
% O God, with our ears have we heard; our fathers have told us.
{Deus, áuribus nostrīs audívimus~; pàtres nostri adnunçiavérunt nobīs.}
{Exsùrge, Dòmine, àdjuva nos.}
{Et rèdime nos pròpter nomen tuum.}\vspaceLarge

\antiphonDayOfWeek
{Domìnica V,}
{Psàlmus IX.}
{in tono quìnto~:}
% Arise, O Lord God; let your hand be lifted up. The Lord reigns forever.
{Exsùrge, Dòmine Deus~; exaltétur mànus tua~; Dòminus regnábit in aetèrnum.}
% I will confess to you, O God, with my whole heart. I Will tell of all your wonders.
{Confitébor tìbi, Dòmine, in toto corde meo~; narrábo òmnia mirabìlia tua.}
{Exsùrge, Dòmine Deus~; exaltétur mànus tua.}
{Dòminus regnábit in aetèrnum.}\vspaceLarge

\antiphonDayOfWeek
{Domìnica VI,}
{Psàlmus LXXIX.}
{in tono sèxto~:}
% Stir up your power, and come so that we may be saved.
{Èxčita potènçiam tuam, et vèni ut sàlvos fàčias nos.}
% Who rules Israel, attend, who leads Joseph as a sheep.
{Qui reǧis Israélem, intènde, qui dedúcis vèlut ovem Joséfum.}
{Èxčita potènçiam tuam.}
{Et vèni ut sàlvos fàčias nos.}\vspaceLarge

\newpage

\antiphonDayOfWeek
{Domìnica VII,}
{Psàlmus IX.}
{in tono sèptimo~:}
% Arise, O Lord God; let your hand be lifted up; do not forget the poor.
{Exsùrge, Dòmine Deus~; exaltétur mànus tua~; ne obliviscáris páuperum.}
% I will confess to you, O God, with my whole heart. I Will tell of all your wonders.
{Confitébor tìbi, Dòmine, in toto corde meo~; narrábo òmnia mirabìlia tua.}
{Exsùrge, Dòmine Deus~; exaltétur mànus tua.}
{Ne obliviscáris páuperum.}\vspaceLarge

\antiphonDayOfWeek
{Domìnica VIII,}
{Psàlmus CXLV.}
{in tono octávo~:}
% The Lord reigns unto the age; your God, Zion, unto generation and generation.
{Regnábit Dòminus in sáecula~; Deus tuus, Zion, in ǧeneraçiónem et ǧeneraçiónem.}
% Praise the Lord, O my soul. I will praise the Lord in my life.
{Lauda, ànima mea, Dòminum. Laudábo Dòminum in vita mea.}
{Regnábit Dòminus in sáecula.}
{Deus tuus, Zion, in ǧeneraçiónem et ǧeneraçiónem.}\vspaceLarge\vspaceSmall

{\hfill \symbolCross \hfill}\vspaceLarge\vspaceSmall



{\hfill \symbolCross \hfill}\vspaceLarge
